TacticToe: Learning the Game of Tactics

### 2018-02-07 tactictoe_jv.tex

\begin{table}[ht]
\centering\ra{1.3}
\small
\begin{tabular}{llc}
\toprule
 Technique & Parameters & Solved \\
\midrule
Tactic time out & 0.02s & 154 (56.8\%)\\
                & 0.05s (default) & 156 (56.8\%)\\
                & 0.1s & 154 (56.0\%)\\
\midrule
Orthogonalization & none & 156 \\
                  & $radius = 10$ & 156 \\
                  & $radius = 20$ (default) & 156 \\
                  & $radius = 40$ & 156 \\

\midrule
Abstraction       & none (default)  & 156 (\%)\\
                  & $theorems = 8$  & 195 (\%)\\
                  & $theorems = 16$ & 199 (72.9\%)\\
                  & $theorems = 32$ & 195 (\%)\\
\midrule
MCTS Policy & $c_{policy} = 0.4$ & 149 (\%)\\
            & $c_{policy} = 0.5$ (default) & 155 (\%)\\
            & $c_{policy} = 0.6$ & 153 (\%)\\
\midrule
MCTS Evaluation & none (default) & 156 (50\%) \\
				& $c_{exploration} = 0.25$ & 153 153 (50\%)\\
				& $c_{exploration} = 0.5$ & 153 155 (50\%)\\
				& $c_{exploration} = 1$ & 154 (50\%)\\
				& $c_{exploration} =\sqrt{2}$ & 154 154 (50\%)\\
				& $c_{exploration} = 2$ & 152 (50\%)\\
\midrule
ATP integration & none (default) & 156 (50\%)\\
                & \metis 0.1s & 125 (50\%)\\
                & \metis 0.2s & 125 (50\%)\\
                & \metis 0.4s & 125 (50\%)\\
                & asynchronous \eprover & 125 (50\%)\\
                & \metis 0.1s + asynchronous \eprover & 190\\
\midrule
All & best parameters (without \eprover) & \\
\bottomrule
\end{tabular}
\end{table}

@@

\todo{decide to keep this section or not}

@@

\begin{table}[h]
\centering\ra{1.3}
\small
\begin{tabular}{lll}
\toprule
 & Additional features & Solved \\
\midrule
$\emptyset$   & none & 119 (43.6\%) \\ %NONEv2
$\mathbb{F}_1$& tactic prediction & 121 (44.3\%) \\ %AFTERTACv2
$\mathbb{F}_2$& token recombination  & 137 (50.2\%) \\ %AFTERTOKENv2
$\mathbb{F}_3$& theorem prediction  & 207 (75.8\%) \\ %AFTERTHMTHMv2
$\mathbb{F}_4$& term prediction & 223 (81.7\%) \\ %AFTERALLv2
$\mathbb{H}$  & all & 239 (87.5\%) \\ %AFTERSMALLv2
% $AFTERv2$       & $\mathfrak{H}$ & 245 (89.7\%)  \\
\bottomrule
\end{tabular}
\caption{\label{tab:featue_param} Effect of augmenting \tactictoe's knowledge
with tactics from the proof of the tested theorem. The experiments was run with
a time out of 5 seconds on an older version of \tactictoe, as can be seen in
the low
success rate of the
default strategy.}
\end{table}

>>>>

\begin{table}[ht]
\centering\ra{1.3}
\small
\begin{tabular}{llcc}
\toprule
 Technique & Parameters & Solved (1s) & Solved (60s)\\
\midrule
Tactic time out & 0.02s && 154\\
                & 0.05s (default) && 156\\
                & 0.1s && 154\\
\midrule
Orthogonalization & none & 105 & 156 \\
                  & $radius = 10$ & 121 & 156 \\
                  & $radius = 20$ (default) & 121 & 156 \\ 
                  & $radius = 40$ & 124 & 156 \\
\midrule
Abstraction       & none (default)  && 156\\ 
                  & $theorems = 8$  && 195\\
                  & $theorems = 16$ && 199\\
                  & $theorems = 32$ && 195\\
\midrule
MCTS policy & $c_{policy} = 0.4$ && 149\\
            & $c_{policy} = 0.5$ (default) && 156\\
            & $c_{policy} = 0.6$ && 153\\
\midrule
MCTS evaluation & none (best abstraction) && 199\\
				& $c_{exploration} = 1$ && 201\\ 
				& $c_{exploration} = 2$ && 203\\ 
				& $c_{exploration} = 4$ && 198\\
\midrule
ATP integration & none (best MCTS evaluation) && 203\\
                & \metis 0.1s && 216\\
                & \metis 0.2s && 212\\
                & \metis 0.4s && 212\\ 
                & \eprover && 213\\
                & \metis 0.1s + \eprover && 218\\
\bottomrule
\end{tabular}
\caption{\label{tab:tuning} Number of problem solved with different set of 
parameters for \tactictoe on a training set of 273 theorems.} 
\end{table}

@@

@@

\begin{table}[h]
\centering\ra{1.3}
\small
\begin{tabular}{lll}
\toprule
 & Additional features & Solved \\
\midrule
$\emptyset$   & none & 119 (43.6\%) \\ %NONEv2
$\mathbb{F}_1$& tactic prediction & 121 (44.3\%) \\ %AFTERTACv2
$\mathbb{F}_2$& token recombination  & 137 (50.2\%) \\ %AFTERTOKENv2
$\mathbb{F}_3$& theorem prediction  & 207 (75.8\%) \\ %AFTERTHMTHMv2
$\mathbb{F}_4$& term prediction & 223 (81.7\%) \\ %AFTERALLv2
$\mathbb{H}$  & all & 239 (87.5\%) \\ %AFTERSMALLv2
% $AFTERv2$   & $\mathfrak{H}$ & 245 (89.7\%)  \\
\bottomrule
\end{tabular}
\caption{\label{tab:featue_param} Effect of augmenting \tactictoe's knowledge 
with tactics from the proof of the tested theorem. The experiments was run 
with 
a time out of 5 seconds on an older version of \tactictoe, as can be seen in 
the low success rate of thedefault strategy.} 
\end{table}
